A Fast and Tight Heuristic for A* in Road Networks

### 2021-10-15 paper/ch_potentials.tex
some discussion of valentins results

>>>>

In this section, we report the results of the k-Nearest-Neighbor Queries on CCH with Lazy RPHAST.
The authors of~\cite{buchhold_et_al:LIPIcs.SEA.2021.18} provide the code for their algorithm and their experiments on Github\footnote{\url{https://github.com/vbuchhold/routing-framework}}.
This includes the code for both the old version and the new one improved with Lazy RPHAST.
We reran the experiments performed for~\cite{buchhold_et_al:LIPIcs.SEA.2021.18} in both the old and the new configuration on our machine.
In the results, we denote the old version as \emph{CCH/CRAD} and the new one as \emph{CCH*/CRAD*}.
Our results exhibit the same characteristics as observed in the original publication.
Absolute running times of course vary slightly.

Lazy RPHAST yields the greatest improvements of more than an order of magnitude when the points of interest (\emph{POIs}) are concentrated in a smaller region (see Table~\ref{tab:knn} and Figure~\ref{fig:knn_ball_size}).
When the POIs are distributed over the whole graph, the speed-up is only around factor of three.
Lazy RPHAST also achieves greater speed-ups for larger numbers of POIs (see Figure~\ref{fig:knn_num_pois}).
For the demand generation application, this translates to a speed-up factor of around 2.5 (see Figure~\ref{fig:knn_demands}).
For a more detailed discussion of these results and a comparison to competing algorithms, we refer to~\cite{buchhold_et_al:LIPIcs.SEA.2021.18}.
